|

### 2021-01-25 supplementary_information.Rmd
Update supplementary_information.Rmd

## Table S3 Sensitivity analysis for the effect of ecosystem size

@@

## Table S4 Sensitivity analysis for the effect of ecosystem complexity

@@

**Figure S19 ** Correlation structure of potential explanatory variables for riverine diversity metrics. Positive and negative correlations were colored in blue and red, respectively, and darker colors indicate stronger correlations. Environmental variables (temperature, precipitation, elevation, logit fraction of forest, logit fraction of urban, logit fraction of agriculture, and dam density) were expressed as deviations from regional averages to remove any regional effects.

>>>>

## Table S3 Sensitivity analysis for ecosystem size effects

@@

## Table S4 Sensitivity analysis for ecosystem complexity effects

@@

**Figure S19 ** Correlation structure of potential explanatory variables for riverine diversity metrics. Positive and negative correlations were colored in blue and red, respectively, and darker colors indicate stronger correlations. Environmental variables (temperature, precipitation, elevation, logit fraction of forest, logit fraction of urban, logit fraction of agriculture, and dam density) were expressed as deviations from the regional averages to remove any regional effects.
